A Decision Procedure for (Co)datatypes in SMT Solvers\thanks{In memoriam Morgan Deters 1979--2015}

### 2016-04-16 sister/sister.tex
Fixes for submission.

\documentclass[letter]{article}
% The file ijcai16.sty is the style file for IJCAI-16 (same as ijcai07.sty).
\usepackage{ijcai16}

\usepackage[T1]{fontenc}
\usepackage{flushend}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[scaled=.82]{beramono}
\usepackage[scaled=.86]{helvet}
\usepackage{booktabs}
\usepackage{bussproofs}
%\usepackage{cite}
\usepackage{color}
\usepackage{mathptmx}
\usepackage{mathpartir}
\usepackage{stmaryrd}
\usepackage{subfigure}
\usepackage{textcomp}
\usepackage{url}
\usepackage[all]{xy}

@@

%%% For final version as well?
\usepackage[
   a4paper,
   pdftex,
   pdftitle={A Decision Procedure for (Co)datatypes in SMT Solvers},
   pdfauthor={Andrew Reynolds and Jasmin Christian Blanchette},
   pdfkeywords={},
   pdfborder={0 0 0},
   draft=false,
   bookmarksnumbered,
   bookmarks,
   bookmarksdepth=2,
   bookmarksopenlevel=2,
   bookmarksopen]{hyperref}

>>>>

\documentclass[letter]{article}
% The file ijcai16.sty is the style file for IJCAI-16 (same as ijcai07.sty).
\usepackage{ijcai16}
\usepackage{times}

\usepackage[T1]{fontenc}
%\usepackage{flushend}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[scaled=.82]{beramono}
\usepackage[scaled=.86]{helvet}
\usepackage{booktabs}
\usepackage{bussproofs}
%\usepackage{cite}
\usepackage{color}
\usepackage{mathptmx}
\usepackage{mathpartir}
\usepackage{stmaryrd}
\usepackage{subfigure}
\usepackage{textcomp}
\usepackage{url}
\usepackage[all]{xy}

@@

%%% For final version as well?
%\usepackage[
%   a4paper,
%   pdftex,
%   pdftitle={A Decision Procedure for (Co)datatypes in SMT Solvers},
%   pdfauthor={Andrew Reynolds, Jasmin Christian Blanchette},
%   pdfkeywords={Decision Procedures, Automated Theorem Proving, Satisfiability Modulo Theories},
%   pdfborder={0 0 0},
%   draft=false,
%   bookmarksnumbered,
%   bookmarks,
%   bookmarksdepth=2,
%   bookmarksopenlevel=2,
%   bookmarksopen]{hyperref}

\pdfinfo{
  /Title (A Decision Procedure for (Co)datatypes in SMT Solvers)
  /Author (Andrew Reynolds, Jasmin Christian Blanchette)
  /Keywords (Decision Procedures, Automated Theorem Proving, Satisfiability Modulo Theories)
}
